*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "splitByExperiment" into "split_by_experiment";

allows for the complete generation of the PPR plot in publication quality from 
the user assembled spreadsheet of input data (`x`), including automatically 
added graphical representations the PPR value equal to the fit constant 
$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average 
carrying one scramblase and 63% have one or more 
[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
adjusted to use scramblase-mediated fluorescence reduction normalized to either
the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
exponential fit to it (`scale_to = "model"`; for reasoning see above) and whether
or not to require the exponential curve fitted to the data to go through the
origin. The `splitByExperiment` argument is used to indicate whether independent
experiments are integrated into a single analysis (`splitByExperiment = FALSE`)
or treated separately (`splitByExperiment = TRUE`; see below for example usage).

@@

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
x <- flippant:::readScramblaseInputFile(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 1,
  bottomPanel = 3,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblase_assay_traces(x, timeMaxSec = 350) + theme_bw())
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 4,
  bottomPanel = 5,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 6,
  bottomPanel = 7,
  leftPanel = 1,
  rightPanel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  splitByExperiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 1,
  splitByExperiment = FALSE) + 
xlim(0, 2)
```

@@

```{r, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, splitByExperiment = FALSE)
```

```{r, echo = FALSE}
ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, splitByExperiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    timeMaxSec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    splitByExperiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 1, 
    splitByExperiment = FALSE)
}

>>>>

allows for the complete generation of the PPR plot in publication quality from 
the user assembled spreadsheet of input data (`x`), including automatically 
added graphical representations the PPR value equal to the fit constant 
$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average 
carrying one scramblase and 63% have one or more 
[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
adjusted to use scramblase-mediated fluorescence reduction normalized to either
the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
exponential fit to it (`scale_to = "model"`; for reasoning see above) and whether
or not to require the exponential curve fitted to the data to go through the
origin. The `split_by_experiment` argument is used to indicate whether independent
experiments are integrated into a single analysis (`split_by_experiment = FALSE`)
or treated separately (`split_by_experiment = TRUE`; see below for example usage).

@@

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
x <- flippant:::readScramblaseInputFile(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 1,
  bottomPanel = 3,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblase_assay_traces(x, timeMaxSec = 350) + theme_bw())
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 4,
  bottomPanel = 5,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 6,
  bottomPanel = 7,
  leftPanel = 1,
  rightPanel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 1,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

@@

```{r, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, split_by_experiment = FALSE)
```

```{r, echo = FALSE}
ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, split_by_experiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    timeMaxSec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    split_by_experiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 1, 
    split_by_experiment = FALSE)
}
